Group meetings

### 2023-06-26 diapo/26-06-23_meeting/main.tex
Finished juin 26 pres

\documentclass[table]{beamer}
\usetheme{gpmeet}
\graphicspath{{../../figures/}}

@@

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{3cm} c m{3cm} c }
    \rowcolor{firstRow}
    \color{white}\textbf{\#} & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
    1 & Try to use LTSpice & No & Found out I could do what I want with Cadence & No\\
    2 & Find another\newline problem to work on & No & Lack of time & Yes\\
    3 & Work on the thesis intro & on going &  & No\\
  \end{tabular}

@@

\begin{frame}{What's new}
  \begin{itemize}
    \item Results obtianed :
      \begin{itemize}
          \color{text}
        \item With the help of Fabio, I can now simulate all the steps automatically
        \item I successfully ran the simulation
        \item The result are not correct
      \end{itemize}
    \item Improvements :
      \begin{itemize}
          \color{text}
        \item Debug the whole thing
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{What's new}
  \includegraphics[width=\textwidth]{fulltrial1/fulltrial1-all-curves}
\end{frame}

\begin{frame}<1>[label=prob]
  \frametitle{Problems/doubts}
  \begin{itemize}
    \item<1-> The memory doesn't output the right values
    \item<2-> The memory input seems to be active for too long
    \item<3-> The output of the sigmoid doesn't look right
    \item<4-> The output result isn't what is expected
  \end{itemize}
\end{frame}

\begin{frame}{Problems/doubts}
  The memory doesn't output the right values.

  \centering
  \includegraphics[width=0.7\textwidth]{fulltrial1/fulltrial1-memory-prob}
\end{frame}

\againframe<2>{prob}

\begin{frame}{Problems/doubts}
  \centering
  \includegraphics[width=1\textwidth]{fulltrial1/fulltrial1-mem-act-late}
\end{frame}

\againframe<3>{prob}
\begin{frame}{Problems/doubts}
  Here we can see that the output of the sigmoid isn't right
  \begin{figure}[!tbp]
    \centering
    \begin{minipage}[b]{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{fulltrial1/sigmoid-prob.png}
    \end{minipage}
    \hspace{20pt}
    \begin{minipage}[b]{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{activation/sigmoid-prob}
    \end{minipage}
  \end{figure}
\end{frame}

\againframe<4>{prob}
\begin{frame}{Problems/doubts}
  The output is ~0.791 V. This is $-1.09$ and should be $0.015$

  \centering
  \includegraphics[width=\textwidth]{fulltrial1/fulltrial1-final-res}
\end{frame}

@@

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{4cm} }
    \rowcolor{firstRow}
    \color{white}\textbf{\#} & \centering\color{white}Task \cr
    1 & Find another LSTM problem \\
    2 & "Debug" the circuit \\
    2.1 & Run the entire simulation \\
    3 & Work on thesis \\
  \end{tabular}
\end{frame}

\begin{frame}{Networking and sharing}
  \begin{tikzpicture}
    \leftRect{Help/Collaboration :}{- If anybody has any idea of an interesting LSTM/NN problem to work on.\\-Also if any phenomen happening are familiar to you, I'll take the help\\- I would need the feature size of a typical memristor}

    \rightRect{Recommendations :}{I worked on a latex/beamer version of the template}
  \end{tikzpicture}
\end{frame}

>>>>

\documentclass[table]{beamer}
\usetheme{gpmeet}
\setbeamertemplate{caption}{\raggedright\insertcaption\par}
\graphicspath{{../../figures/}}

@@

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{ c m{4cm} c m{2cm} c }
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
      1 & Find another LSTM problem & On going & Didn't find & Yes\\
      2 & Find out what is causing the issue & Partly & I had a scale of 10 000 and reduced it to 1.5 & No\\
      3 & Find formula for approximate onChip area & No & Can be done later & No\\
      4 & Work on thesis & On going & & No\\
    \end{tabular}

@@

  \begin{frame}{What's new}
    \begin{itemize}
      \item Results obtianed :
        \begin{itemize}
            \color{text}
          \item I reduced the factor of the results
          \item The factor is now tolerable, will have to see how it behaves with other problems
        \end{itemize}
      \item Improvements :
        \begin{itemize}
            \color{text}
          \item Reduce the still existing factor
        \end{itemize}
      \item Relevant information :
        \begin{itemize}
            \color{text}
          \item I reduced the factor to 16 first, and then to 1.5.
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}{What's new}
    Here the scale factor is almost the same with the serialized and parallel version ( 1.50 vs 1.58 ).
    \includegraphics[width=\textwidth]{output/factor1.5.png}
  \end{frame}

  \begin{frame}
    \frametitle{Problems/doubts}
    \begin{itemize}
      \item The results are still not quite right.
      \item I am wondering whether it is still due to the activation function circuit.
    \end{itemize}
  \end{frame}

  \begin{frame}{Problems/doubts}
    I had to train using custom activation function but still not perfect.
    \begin{figure}[!tbp]
      \centering
      \begin{minipage}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{activation/sigmoid}
        \caption{ $Sigmoid(x)$ - RSME : 0.0051}
      \end{minipage}
      \hspace{20pt}
      \begin{minipage}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{activation/cSigmoid}
        \caption{ $ Sigmoid(0.67\cdot x) $ - RSME : 0.0014}
      \end{minipage}
      \caption{Sigmoid}
    \end{figure}
  \end{frame}

  \begin{frame}{Problems/doubts}
    I had to train using custom activation function but still not perfect.
    \begin{figure}[!tbp]
      \centering
      \begin{minipage}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{activation/tanh}
        \caption{ $ Tanh(x) $ - RSME : 0.022}
      \end{minipage}
      % \rightarrow
      \hspace{20pt}
      \begin{minipage}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{activation/cTanh}
        \caption{ $2\cdot Sigmoid(0.67\cdot x)-1$ - RSME : 0.0029}
      \end{minipage}
      \caption{Tanh}
    \end{figure}
  \end{frame}

@@

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{ c m{6cm} }
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task \cr
      0 & Work on thesis \\
      0.1 & Formula onChip Area \\
      1 & Find another LSTM problem \\
      2 & Try to reduce the scale factor again \\
      2.1 & Tensorflow custom function \\
    \end{tabular}
  \end{frame}

  \begin{frame}{Networking and sharing}
    \begin{tikzpicture}
      \leftRect{Help/Collaboration :}{- If anybody has any idea of an interesting LSTM/NN problem to work on.}

      \rightRect{Recommendations :}{None}
    \end{tikzpicture}
  \end{frame}
